### 2014-10-31 fundamentals/impl.tex
went with plug-in, cuz google said so.

The core of the \Cyclus simulator creates a set of key classes on which agent plugins 
are based. In addition, a set of key tools are also provided to enrich the 
\gls{API} and supply a robust suite of behaviors for the developer.

@@

Agent plugins utilize the generic core \gls{API} to interact with one another.  For 
example, agents rely on the dynamic loading and paradigm for clean plugin 
behavior at the start of the simulation. They also use the resource exchange 
paradigm \gls{API} for trading resources with one another.

@@

A key innovation in \Cyclus is implementing this generic \gls{API} and modular 
architecture into a suite of dynamically loadable ``plugin'' libraries.  Though 
common in modern software architecture, such a ``plugin'' pattern has 
previously not been implemented in nuclear fuel cycle simulators in the 
literature.  In \Cyclus, this implementation maximizes the potential of the clean, 
object-oriented \gls{API} and modern build system already described.

Dynamically loadable libraries are the primary mechanism for extending \Cyclus' capability. 
This approach provides encapsulation: the core of the code operates
completely independently from the individual plugin libraries. Thus, any
customization or extension is implemented only in the loadable
library.

@@

In particular, since the clean plugin architecture loads libraries without any
modifications to the \Cyclus kernel, closed-source archetypes can be used with
the simulator alongside open-source archetypes. This architecture
allows closed-source libraries (e.g., those representing sensitive nuclear
processes and subject to export control) to be developed and licensed privately.

@@

Due to this ``plugin'' architecture,
implementations of actors in a given simulation can be easily
interchanged. Critically, this novel functionality enables the comparison
between agent implementations. For example, a low-physics-fidelity
implementation of a reactor can be compared to an implementation with higher
physics fidelity, allowing an analyst to discern the effect of reactor physical
fidelity on a given fuel cycle.

>>>>

The core of the \Cyclus simulator creates a set of key classes on which agent 
plug-ins 
are based. In addition, a set of key tools are also provided to enrich the 
\gls{API} and supply a robust suite of behaviors for the developer.

@@

Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For 
example, agents rely on the dynamic loading and paradigm for clean plug-in 
behavior at the start of the simulation. They also use the resource exchange 
paradigm \gls{API} for trading resources with one another.

@@

A key innovation in \Cyclus is implementing this generic \gls{API} and modular 
architecture into a suite of dynamically loadable plug-in libraries.  Though 
common in modern software architecture, such a plug-in pattern has 
previously not been implemented in nuclear fuel cycle simulators in the 
literature.  In \Cyclus, this implementation maximizes the potential of the clean, 
object-oriented \gls{API} and modern build system already described.

Dynamically loadable libraries are the primary mechanism for extending \Cyclus' capability. 
This approach provides encapsulation: the core of the code operates
completely independently from the individual plug-in libraries. Thus, any
customization or extension is implemented only in the loadable
library.

@@

In particular, since the clean plug-in architecture loads libraries without any
modifications to the \Cyclus kernel, closed-source archetypes can be used with
the simulator alongside open-source archetypes. This architecture
allows closed-source libraries (e.g., those representing sensitive nuclear
processes and subject to export control) to be developed and licensed privately.

@@

Due to this plug-in architecture,
implementations of actors in a given simulation can be easily
interchanged. Critically, this novel functionality enables the comparison
between agent implementations. For example, a low-physics-fidelity
implementation of a reactor can be compared to an implementation with higher
physics fidelity, allowing an analyst to discern the effect of reactor physical
fidelity on a given fuel cycle.
